Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
shortened captions

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/dc_hierarchical_speedup.pdf}
\caption{Strong Scaling for Clustering on \hyper{}}
\label{fig:dcspeedup}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_sequential_level_breakdown.pdf}
\caption{Level Timings for 1 Compute Node on Synthetic}
\label{fig:seqlevelbreakdown}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_parallel_level_breakdown.pdf}
\caption{Level Timings for 40 Compute Nodes on Synthetic}
\label{fig:parallellevelbreakdown}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=.7\columnwidth]{plots/dc_hierarchical_speedup.pdf}
\caption{Strong Scaling for Clustering on \hyper{}}
\label{fig:dcspeedup}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_sequential_level_breakdown.pdf}
\caption{Level Times for 1 Compute Node on Synthetic}
\label{fig:seqlevelbreakdown}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_parallel_level_breakdown.pdf}
\caption{Level Times for 40 Compute Nodes on Synthetic}
\label{fig:parallellevelbreakdown}
\end{center}
\end{figure}
